Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-24 paper/paper.tex
Regular things

>>>>

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(10, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(20, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(30, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-30-150.pdf}}; &
            \\
        };
    \end{tikzpicture}

    \caption{Behaviour of algorithms on random $k$-regular graphs, as the pattern degree (x-axis)
    and target degree (y-axis) are varied from 0 to $\left|\operatorname{V}\right| - 1$.}
    \label{figure:kr}
\end{figure}

By $\mathcal{G}(n, k)$ we mean a random graph with $k$ vertices, each of which has degree $k$. In
\cref{figure:kr} we recreate \cref{figure:non-induced}, using the NetworkX implementation
\citep{NetworkX} of the \citet{DBLP:journals/cpc/StegerW99} algorithm to generate regular graphs.
The $x$-axes range from degree 0 to degree $n - 1$, and the y-axes range from degree 0 to degree
149.
